%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%                                                                 %
%%%%%     01_introduction.tex                                         %
%%%%%                                                                 %
%%%%% Author:      Miguel Correa, Elio Warner                         %
%%%%% Created:     22.03.2024                                         %
%%%%% Description: - Overview of the Croc SoC and its open-source     %
%%%%%                nature                                           %
%%%%%              - Why a watchdog timer (WDT) was needed            %   
%%%%%              - Goals and expected improvements                  %
%%%%%                                                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Introduction}
\label{chap:introduction}

\section{Overview of the Croc SoC}
CROC SoC is a lightweight, open-source system-on-chip designed for education and rapid prototyping. It provides a complete RTL-to-GDSII flow and basic processor and peripheral infrastructure, and even includes an explicit user\_domain where students can add and test their own modifications. As a relatively new project, CROC isn’t yet fully optimized, leaving ample room to enhance its reliability, performance, and feature set.

\section{Motivation for Watchdog Integration}
TODO: ADD SOURCE NASA
\\
In May 1994, the NASA Clementine lunar probe suffered a critical onboard computer failure shortly after departing lunar orbit. A malfunction caused one of its thrusters to fire uncontrollably, spinning the spacecraft at 80 rpm until it exhausted its remaining fuel. NASA was able to bring Clementine back online with a manual reset command, but only after the mission’s continuation toward its asteroid target had become impossible. As it later emerged, just a few lines of watchdog-timer code—hard-wired into the flight computer—would have detected the hang, issued an automatic reset immediately, and prevented the thruster runaway that doomed the asteroid rendezvous.
\\
Likewise, in the CROC SoC environment—where students routinely extend the design with custom peripherals and firmware—undetected hangs or deadlocks can leave the chip in an unusable state. Embedding a hardware watchdog ensures that any such fault triggers an automatic reset to a known-good state, dramatically improving system robustness and streamlining recovery during both development and tape-out testing.

\section{Project Objectives}
This project aims to design and integrate a simple yet effective hardware watchdog timer into the CROC SoC, with the following objectives:
\begin{itemize}
  \item{Reliable Fault Detection:} Detect processor stalls or bus deadlocks within a bounded timeout period.
  \item{Automatic Recovery:} Trigger a chip-wide reset when the watchdog expires, returning the system to a known-good state.
  \item{Minimal Overhead:} Add the watchdog with low area, timing, and power impact, preserving CROC’s lightweight footprint.
\end{itemize}
With these goals, the watchdog integration will bolster CROC’s robustness without compromising its simplicity or educational value.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../report_template"
%%% End: 
